---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r}
library(tidyverse)
library(p8105.datasets)

library(plotly)
```

Trim down the dataset

```{r}
data(nyc_airbnb)

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(rating = review_scores_location / 2) |>
  select(
    neighbourhood_group, neighbourhood, rating, price, room_type, lat, long) |>
  filter(
    !is.na(rating), 
    neighbourhood_group == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500)
```

# Scatterplot

Below we’re plotting the location (latitude and longitude) of the rentals in our dataset, and mapping `price` to color. We also define a new variable `text_label` and map that to text.

The type of plot is `scatter`, which has several “modes”: `markers` produces the same kind of plot as `ggplot::geom_point`, `lines` produces the same kind of plot as `ggplot::geom_line`.

This can be a useful way to show the data – it gives additional information on hovering and allows you to zoom in or out, for example.

```{r}
nyc_airbnb |>
  mutate(text_label = str_c("Price: $", price, "\nRating: ", rating)) |> 
  plot_ly(
    x = ~lat, y = ~long, type = "scatter", mode = "markers",
    color = ~price, text = ~text_label, alpha = 0.5)
```

# Boxplot

```{r}
nyc_airbnb |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  plot_ly(y = ~price, color = ~neighbourhood, type = "box", colors = "viridis")
```


# Barchart

```{r}
nyc_airbnb |> 
  count(neighbourhood) |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) |> 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood, type = "bar", colors = "viridis")
```

# Convert ggplot to plotly (interactive plot)

```{r}
scatter_ggplot = 
  nyc_airbnb |>
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = 0.25) +
  coord_cartesian()

ggplotly(scatter_ggplot)
```

```{r, eval = FALSE}
box_ggplot = 
  nyc_airbnb |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  ggplot(aes(x = neighbourhood, y = price, fill = neighbourhood)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggplotly(box_ggplot)
```








